### 2021-06-09 paper/report.tex
Done for the night. Lacking last couple of paragraphs, abstract, description undetected cases, small stuff.

% \clearpage

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity
on many dimensions. The development of highly effective vaccines holds the promise of
containment in the medium term. However, most countries find themselves many
months---and often years---away from reaching vaccination-induced herd immunity
\citep{Swaminathan2021}.\comment[id=K]{WHO Press Conference saying we won't reach herd
immunity in 2021} In the meantime, it is of utmost importance to employ an effective mix
of strategies for containing the virus. The most frequent initial response was a set of
non-pharmaceutical interventions (NPIs) to reduce contacts between individuals. While
this has allowed some countries to sustain equilibria with very low infection
numbers\footnote{See \citet{Contreras2021} for a theoretical equilibrium at low case
numbers which is sustained with test-trace-and-isolate policies.}, most have seen large
fluctuations of infection rates. Containment measures have become increasingly diverse
and now include testing, more nuanced NPIs, and contact tracing. Neither these policies'
effect nor the influence of seasonal patterns or more infectious virus strains are well
understood in quantitative terms. This paper develops a model incorporating all these
factors. The framework allows to combine a wide variety of data in a timely fashion,
making it useful to predict the effects of various interventions. We apply the model to
Germany and show that rapid testing had the largest impact on the reduction in
infections by almost 80\% during the month of May 2021. We conclude that rapid tests
have a large role to play at least as long as vaccinations have not been offered to an
entire population.

@@

The model includes several other features, which are crucial to describe the evolution
of the pandemic in 2020-2021. New virus strains with different profiles regarding
infectiousness can be introduced. Agents may receive a vaccination. With a probability
of 75\% \citep{Hunter2021}, vaccinated agents become immune and they do not transmit the
virus \citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.\comment[id=T]{Maybe add
that 35\% reach immunity after two weeks and 40\% after three weeks.}\footnote{75\% is
lower than what is usually reported for after the second dose of the Biontech/Pfizer
vaccine, which is most commonly used in Germany. We choose it because our model neither
includes booster shots, nor does it allow vaccinated individuals who became immune to
transmit the disease \citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.} During
the vaccine roll-out, priority may depend on age and occupation.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/full_decomposition_channels_area}
        \includegraphics[width=\textwidth]{../figures/results/figures/full_decomposition_channels_bar}

        \vskip2ex

        \caption{Decomposition of effects for
            Figure~\ref{fig:2021_scenarios_newly_infected}.}
        \label{fig:2021_scenarios_decomposition}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

        \includegraphics[width=\textwidth]{../figures/results/figures/full_decomposition_rapid_tests_area}
        \includegraphics[width=\textwidth]{../figures/results/figures/full_decomposition_rapid_tests_bar}
        \caption{{Effects of different types of testing}}
        \label{fig:2021_scenarios_decomposition_tests}
    \end{subfigure}

@@

The largest effect---almost one half when considering the decompositions---comes from
rapid testing. Here, it is crucial to differentiate between recorded cases and actual
cases. Additional testing means that infections become known which would otherwise
remain undetected. Figure~\ref{fig:2021_scenarios_recorded} shows that this means that
until late April, recorded cases are higher than in the scenario where none of the three
mechanisms is turned on. Compared to the scenario with vaccinations only, this point is
reached around mid-May and it would be June for the comparison with the seasonality-only
scenario. The effect on total cases, however, is visible immediately. Despite the fact
that only a small fraction of the population performed weekly rapid tests in
March\footnote{X\% in the model; 27\% of respondents to the COSMO study reported in
early March that they \textit{ever} did a rapid test)}\comment[id=HM]{Put in}, new
infections on April 1 would be rise in new infections would be reduced by 53\% relative
to the scenario without vaccinations, rapid tests, or seasonality.

Two of the most contentious NPIs concern schools and mandates to work from home. In many
countries, schools switched to remote instruction during the first wave, so did Germany.
They were kept fully open until Two particularly important areas:
\begin{itemize}
    \item Schooling: large costs to pupils, ... social inequalities
    \item Work: Q2 / 2020 saw the largest drop in GDP in a long time;
\end{itemize}

Results
\begin{itemize}
    \item Advantage of testing in both cases: Recurrent. Small cost relative to other
          stuff. Certain publicness.
    \item Mandatory tests: Screening effect: ...
\end{itemize}

@@

\paragraph{Points to mention}
\begin{itemize}
    \item If anything too optimistic regarding vaccinations
    \item Social structure / conditional block testing in families important (?)
    \item Trump-effect: More testing = more cases true for how long?
    \item Towards the end, total tests go down: Preferences for tests remain the same,
          but infection rates lower \comment[id=HM]{Janos, please fill up}
    \item Actually performed tests increase until May, stay constant during May and then
    start to drop
    \item This is the combination of the following things:
          \begin{itemize}
              \item time constant willingness to take tests
              \item monotonically increasing availability of tests
              \item endogenous number of situations in which a test should be taken
              (mainly positive tests of household members)
          \end{itemize}
    \item This is a classic way of modeling in economics: Preferences stay constant (and
          can thus be elicited in just one survey) but outcomes change because
          circumstances change.

\end{itemize}

An important feature of the way we model rapid tests is that the number of actually
performed test is determined endogenously. The number of weekly tests increases until
the end of May and then starts to drop. This is because many  It is determined by the
availability of tests, the individual compliance with testing recommendations and the
occurrence of situations in which a test should be taken.

% Technical terms should be defined.

% Symbols, abbreviations, and acronyms should be defined the first time they are used.

% All tables and figures should be cited in numerical order.

% All data must be shown either in the main text or in the Supplementary Materials or
% must be available in an established database with accession details provided in the
% acknowledgements section.

% References to unpublished materials are not allowed to substantiate significant
% conclusions of the paper.

>>>>

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity
on many dimensions. The development of highly effective vaccines holds the promise of
containment in the medium term. However, most countries find themselves many
months---and often years---away from reaching vaccination-induced herd immunity
\citep{Swaminathan2021}.\comment[id=K]{WHO Press Conference saying we won't reach herd
immunity in 2021}\comment[id=HM]{If we find a paper (s)he cites, would be even better}
In the meantime, it is of utmost importance to employ an effective mix of strategies for
containing the virus. The most frequent initial response was a set of non-pharmaceutical
interventions (NPIs) to reduce contacts between individuals. While this has allowed some
countries to sustain equilibria with very low infection numbers\footnote{See
    \citet{Contreras2021} for a theoretical equilibrium at low case numbers which is
    sustained with test-trace-and-isolate policies.}, most have seen large fluctuations of
infection rates. Containment measures have become increasingly diverse and now include
testing, more nuanced NPIs, and contact tracing. Neither these policies' effect nor the
influence of seasonal patterns or more infectious virus strains are well understood in
quantitative terms. This paper develops a model incorporating all these factors. The
framework allows to combine a wide variety of data in a timely fashion, making it useful
to predict the effects of various interventions. We apply the model to Germany and show
that rapid testing had the largest impact on the reduction in infections by almost 80\%
during the month of May 2021. We conclude that rapid tests have a large role to play at
least as long as vaccinations have not been offered to an entire population.

@@

The model includes several other features, which are crucial to describe the evolution
of the pandemic in 2020-2021. New virus strains with different profiles regarding
infectiousness can be introduced. Agents may receive a vaccination. With a probability
of 75\% \citep{Hunter2021}, vaccinated agents become immune and they do not transmit the
virus \citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}.\comment[id=T]{Maybe add
that 35\% reach immunity after two weeks and 40\% after three weeks.}\footnote{75\% is
    lower than what is usually reported for after the second dose of the Biontech/Pfizer
    vaccine, which is most commonly used in Germany. We choose it because our model neither
    includes booster shots, nor does it allow vaccinated individuals who became immune to
    transmit the disease\citep{Petter2021, LevineTiefenbrun2021, Pritchard2021}. If
    anything, these assumptions would overstate the effect of vaccines for our study period.
    This would be different if a large fraction of vaccinated individuals had received a
    second dose already.} During the vaccine roll-out, priority may depend on age and
occupation.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/full_decomposition_channels_area}
        % \includegraphics[width=\textwidth]{../figures/results/figures/full_decomposition_channels_bar}
        \caption{Decomposition of the difference between the scenario without any of the
            three factors and the main scenario in
            Figure~\ref{fig:2021_scenarios_newly_infected}.}
        \label{fig:2021_scenarios_decomposition}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/full_decomposition_rapid_tests_area}
        % \includegraphics[width=\textwidth]{../figures/results/figures/full_decomposition_rapid_tests_bar}
        \caption{Decomposition of the difference between the scenario without rapid
            tests and the main scenario in Figure~\ref{fig:2021_scenarios_newly_infected}.}
        \label{fig:2021_scenarios_decomposition_tests}
    \end{subfigure}

@@

The largest effect---almost one half when considering the decompositions---comes from
rapid testing. Here, it is crucial to differentiate between recorded cases and actual
cases. Additional testing means that infections become known which would otherwise
remain undetected. Figure~\ref{fig:2021_scenarios_recorded} shows that this means that
until late April, recorded cases are higher than in the scenario where none of the three
mechanisms is turned on. Compared to the scenario with vaccinations only, this point is
reached around mid-May and it would be June for the comparison with the seasonality-only
scenario. The effect on total cases, however, is visible immediately. Despite the fact
that only a small fraction of the population performed weekly rapid tests in
March\footnote{X\% in the model; 27\% of respondents to the COSMO study reported in
    early March that they \textit{ever} did a rapid test)}\comment[id=HM]{Put in}, new
infections on April 1 would be reduced by 53\% relative to the scenario without
vaccinations, rapid tests, or seasonality.

So why is rapid testing so effective? In order to shed more light on this question,
Figure~\ref{fig:2021_scenarios_decomposition_tests} decomposes the difference in the
scenario without rapid tests only (purple line in
Figure~\ref{fig:2021_scenarios_newly_infected}) and the main specification into the
three channels for rapid tests. Tests for pupils have the smallest effect, which is
largely explained by the relatively small number of students (XXM vs. YYM workers) and
the fact that schools did not operate at full capacity during our period of study.
Almost 40\% come from tests at the workplace. Despite the fact that we phase rapid tests
for private reasons are phased in only late, they make up for more than half of the total effect.

\comment[id=HM]{How many tests are actually performed along each of the three dimensions? Could this be a quantity story rather than the directed testing story I am making up here as wishful thinking?}

The reason lies in the fact that a substantial share of these tests is driven by an
elevated probability to carry the virus, i.e., showing symptoms of CoViD-19 or following
up on a positive test of a household member. The latter is essentially a form of contact
tracing, which has been shown to be very effective.\comment[id=HM]{cite Priesemann
paper, others?} This is also the reason for why the number of tests performed fall at
the very end of our study period. Falling infection rates mean that there are fewer
events triggering private test demand.
\comment[id=HM]{Positive rates along the three channels might be nice here, if previous comment is not a quant story}
\comment[id=HM]{I think there is a story in here about risk conditional on past exposure vs. prospective risk in gatherings, but it is too late to work through it. We might just want to calculate the probabilities.}

Two of the most contentious NPIs concern schools and mandates to work from home. In many
countries, schools switched to remote instruction during the first wave, so did Germany.
After the summer break, they were operating at full capacity with increased hygiene
measures, before being closed again from mid-December on. Some states started opening
them gradually in late February, but usual operaton was not back until the beginning of
June. In light of the large negative effects school closures have on children and
parents\comment[id=HM]{need to cite a couple of poor learning outcomes / mental health
papers. There must be well-published ones}---and in particular on those with low
socio-economic status---

Effects:
\begin{itemize}
    \item Schools were essentially closed
    \item What are the different $R_t$-values? In no-test scenario and $R_t>1$, might be
          worth chopping off 0.05 or whatever that might be?
    \item With tests it is really hard to make a case for that
\end{itemize}

Alternative:
\begin{itemize}
    \item Germany quite lenient on home office relative to other countries (employer had
          to allow)
    \item Testing: Rapid tests are cheap (less than 1\euro), just a nuisance.
\end{itemize}

Results
\begin{itemize}
    \item Advantage of testing in both cases: Recurrent. Small cost relative to other
          stuff. Certain publicness.
    \item Mandatory tests: Screening effect for hard-to-reach populations (do not
          consider in this paper, also due to poor data in DE)
\end{itemize}

@@
